Deriving Multi-Headed Projective Dependency Parses from Link Grammar Parses

### 2014-11-20 doc/LinksToDAG_final.tex
Shrunk the figure 2 graph. Changed the authorship section at the top

\author{Juneki Hong and Jason Eisner
  \\[0.5cm] Department of Computer Science
  \\Johns Hopkins University
  \\Baltimore, MD 21218, USA 
  \\{\tt \{juneki,jason\}@cs.jhu.edu}
}

@@

  %\input{figure/long_parse2.tikz}
  \caption{\small The blue upper edges show CoNLL gold dependency parses; the red lower edges show our oriented version of the link grammar parses. Edges are shown as dotted lines if they appear only in one parse. Edges are highlighted in orange if the child has multiple parents.  Edges that appear in both parses are solid lines, drawn thicker if the directions do not match.  Vertical edges have parent 0.  For 100 example parses, see Appendix~\ref{app:parses} at \url{http://tidyurl.com/LinksToDAG_supplement}.}
  \label{fig:parses}
  \vspace{-6pt}

@@

\begin{figure}[t!]
  \small
  \centering
  \includegraphics[width=\linewidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Convergence to the direction mapping obtained on the largest run.  Precision relative to that run is very high even for small datasets.  Recall grows as more link types are seen.}\label{fig:convergence}
\vspace{-6pt}
\end{figure}

\begin{table*}[ht]
% \renewcommand{\arraystretch}{1.2}    % more space between rows
\hspace*{-1in}
\input{figure/sample_link_analysis_coarse_table.tex}
\caption{Our solution, i.e., our reconstruction of the ``intended'' direction for each link type in the English Link Grammar.  We also indicate the extent to which each of these link types (1) has a single dominant direction, (2) participates in multi-headed constructions, and (3) corresponds to CoNLL links of a predictable direction and type.  For space reasons, we show only the start of this table---the full table can be found in Appendix~\ref{app:linktypes} at \url{http://tidyurl.com/LinksToDAG_supplement}.}\label{tab:linktypes}
\end{table*}

>>>>

\author{
  Juneki Hong \\
  [0.5cm] Language Technologies Institute\\
  Carnegie Mellon University\thanks{Work done while attending Johns Hopkins University}\\
  Pittsburgh, PA 15213, USA\\
  {\texttt{juneki@cs.cmu.edu}}
  \and
  Jason Eisner\\
  [0.5cm] Department of Computer Science\\
  Johns Hopkins University\\
  Baltimore, MD 21218, USA \\
  {\texttt{jason@cs.jhu.edu}}
}

@@

  %\input{figure/long_parse2.tikz}
  \caption{\small The blue upper edges show CoNLL gold dependency parses; the red lower edges show our oriented version of the link grammar parses. Edges are shown as dotted lines if they appear only in one parse. Edges are highlighted in orange if the child has multiple parents.  Edges that appear in both parses are solid lines, drawn thicker if the directions do not match.  Vertical edges have parent 0.  For 100 example parses, see Appendix~\ref{app:parses} of the supplementary material.}
  \label{fig:parses}
  \vspace{-6pt}

@@

\begin{figure}[t!]
  \small
  \centering
  \includegraphics[width=0.7\textwidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Convergence to the direction mapping obtained on the largest run.  Precision relative to that run is very high even for small datasets.  Recall grows as more link types are seen.}\label{fig:convergence}
  \vspace{-6pt}
\end{figure}

\begin{table*}[ht]
% \renewcommand{\arraystretch}{1.2}    % more space between rows
  \hspace*{-1in}
  \input{figure/sample_link_analysis_coarse_table.tex}
  \caption{Our solution, i.e., our reconstruction of the ``intended'' direction for each link type in the English Link Grammar.  We also indicate the extent to which each of these link types (1) has a single dominant direction, (2) participates in multi-headed constructions, and (3) corresponds to CoNLL links of a predictable direction and type.  For space reasons, we show only the start of this table---the full table can be found in Appendix~\ref{app:linktypes} of the supplementary material.}\label{tab:linktypes}
\end{table*}
